\newpage
\subsection*{Statement from \drfull on how he intends to continue work in the United States}

\today
\bigskip

I am the beneficiary of an approved I-140 Immigrant Petition for an Alien Worker
under the EB-1A classification as an individual of extraordinary
ability. I have a vast experience in the field of \dpcs, and I intend to
continue carrying out research in this area in the United States.

I am already employed as a postdoctoral researcher and I conduct research in
the area of my expertise. 
Specifically, I analyze the leakage of sensitive information from de-identified
medical data and develop privacy-preserving methods for data sharing.
I began my work in the United States at Cornell University, and then continued
to conduct research at the New York Genome Center.


After completing my postdoctoral appointment, I plan to apply for professorship
positions in Computer Science at research universities in the United States.
Having become one of the top experts in the field of \dpcs, I believe that I
have a duty to use my expertise to advance the state of the art in privacy
technologies and to share my knowledge with the next generation of
scientists, engineers, and policy-makers in the United States.
I will also continue my presenting research results at international conferences
and serving as a reviewer for conferences and journals in my field.

My research will continue to focus on strengthening privacy protections for
users and improving the cybersecurity posture of computer systems, including
software-update systems and blockchain networks.
I will work on developing mechanisms for private communication and
the private retrieval of information, which, I believe, will become even more in
demand in the future.
I will also continue my work on developing tools for privacy-preserving
analysis and sharing of medical data, which is a field of growing importance in
the upcoming era of personalized medicine.
The National Strategy to Advance Privacy-Preserving Data Sharing and Analytics
highlights the importance of such tools for responsible scientific
research and innovation, especially in healthcare research where data are highly
sensitive and their sharing is limited by the existing regulations.
Obtaining the permanent residency will enable me to
maximize the positive impact of my research and to contribute more significantly
to the United States' innovation ecosystem.

Yours faithfully,

\vspace{4em}
\drfull

\ldots\\
Tel: \ldots\\
E-mail: \ldots

\pagebreak