%!TEX root = ./main.tex
\subsection{Evidence of \drs authorship of scholarly articles in 
	professional or major trade publications or other major media}
\label{sec:authorship}
	
\drs status as a top scientist is further established by his publications in
top-ranked scientific journals and conference proceedings.
To date, \dr has published five peer-reviewed scientific articles, all as
either the first or second author, in international journals and conferences
and has submitted one more publication for peer review to another top journal in
the field.
Enclosed at \citewb{purbs}-\citewb{other_papers} is a selection of
\drs publications.

\textbf{The conferences and journals in which \dr has published his work are the
top, most prestigious venues in his field}, as indicated by factors such as
their high rankings and international program committees staffed by panels of
experts \cite[Metrics of the journals and conferences in which \dr has
published]{venues}.
For example, \dr has several publications in the IEEE Security \& Privacy
Symposium and the USENIX Security Symposium, the top two conferences in the
field of Computer Security \& Cryptography according to the Google
Scholar Metrics ranking~\cite{venues}.
In addition, he has published in the Proceedings on Privacy Enhancing
Technologies and in the ACM Transactions on Embedded Computing Systems, which
are both the premier venues for research into their corresponding topics.

Because of its significant impact in the field, \drs research has been widely
cited by his peers in major scientific publications.
The frequency with which other scholars cite and discuss \drs work is evident
from Google Scholar, the scholarly literature-specific search tool offered by
the Google search engine, which yields impressive \textbf{\numcitations
citations to \drs publications} by other researchers in peer-reviewed articles
and books~\cite[Evidence of the total number of citations
to \drs publications]{gscholar}.
\textbf{These citations are from articles authored by researchers throughout the
United States and in numerous countries around the world.
The fact that \drs research has received such widespread attention all over the
world is a testament to its significance and impact on the field.}

In his \textbf{\uline{independent}} letter of support enclosed at
\citewb{letter-ddd}, \ddd, YY at \yellowuni,
elaborates on the status of the venues in which \dr has published:

\qu{As further evidence of his international recognition in the field,
Dr. Nikitin's work has been published in the most prestigious conferences and
journals, including IEEE Symposium on Security and Privacy,
USENIX Security Symposium, Privacy Enhancing Technologies Symposium, and ACM
Transactions on Embedded Computing Systems.
\textbf{\uline{Due to the fast pace of the field, conferences are the primary
publishing venues for computer security and privacy researchers.}
The conferences in which Dr. Nikitin has published are commonly regarded as the 
most selective and impactful in the field.}
\textbf{Moreover, Dr. Nikitin is a highly cited researcher, meaning that others
in his field have found his work to be novel and useful for their own research.
At this time, his original work has been cited 330 times by researchers from
around the world.} Considering that most scientific papers are scarcely cited,
this is a clear indication of the significant and worldwide impact of Dr.
Nikitin's research.}

\bbb, XX at \reduni, who has closely worked with \dr
on a research project, echoes \drs recognition in the field in his letter of
support enclosed at \citewb{letter-bbb}:

\qu{Dr. Nikitin is an established scientist in computer security and in data and
communication privacy.
\textbf{He has published multiple works in the most prestigious scientific
venues, including top-tier, rigorously peer-reviewed, academic outlets such as
the IEEE Symposium on Security and Privacy and the USENIX Security Symposium.
These venues are extremely selective and attract groundbreaking research from
leading worldwide experts in computer security and privacy.}
The impact of Dr. Nikitin's work is reflected in its significant academic
recognition---his publications have been cited more than 331 times by other
researchers, which is an impressive number for a scientist at his career stage.
This level of citation demonstrates that his contributions are not only relevant
but also influential, shaping ongoing research and advancements in privacy enhancing technologies.}

Finally, another \textbf{\uline{independent}} expert \fff, YY at \whiteuni,
explains the significance of \drs high citation count (see
\citewb{letter-fff}):

\qu{He has publications in top computer security and privacy venues, such as
USENIX Security Symposium and IEEE Symposium on Security and Privacy. 
His work has already received over 300 citations from other scholarly work
(source: Google Scholar), attesting to his influence on the field. 
\textbf{His track record is impressive for his career stage and underscores the
importance and impact of his research work.
His work contributes to both academic research and drives the development of
real-world solutions in data privacy and security.
His contributions to date clearly demonstrate his outstanding ability and
promise considerable benefits to the global community.}}