% \clearpage
\section{\drs proposed employment has both substantial merit and 
national importance for the United States.}
\label{sec:benefit}

\drs proposed employment directly addresses critical challenges in safeguarding
sensitive data and the integrity of digital infrastructure, and mitigating
risks associated with emerging technologies.
His work contributes to the development of innovative solutions for secure data
sharing and privacy-preserving analytics---the key priorities in the National
Strategy to Advance Privacy-Preserving Data Sharing and Analytics~\cite{government}.
In addition to enhancing national security, these solutions bolster public trust
in the digital economy, which is vital for the sustained growth and
competitiveness of the United States on the global stage.

\drs expertise is particularly crucial as cyber threats and data
breaches increasingly target the nation's critical infrastructure, financial
systems, healthcare institutions, and governmental operations. 
By advancing the field of \dpcs, his research supports the objectives outlined
in the Executive Order on Improving the Nation's
Cybersecurity~\cite{government}, which emphasizes the need for robust measures
to protect sensitive systems and information from adversaries. 
His work also aligns with the goals of the Executive Order on America's Supply
Chains, by addressing vulnerabilities in the software supply chain---the key
area of concern for both economic resilience and national defense---and with the
goals of the Executive Order on Strengthening American Leadership in Digital
Financial Technology, by promoting the development of secure and efficient
blockchain technologies (see \citewb{government} for both executive orders).

\textbf{\uline{Independent}} expert \eee, XX at \purpleinc and YY at \cyanuni,
underscores the importance of \drs work in his letter of support enclosed at \citewb{letter-eee}:

\qu{Given my expertise and service to the U.S. government, I believe that I am
well-qualified to assess Dr. Nikitin's extraordinary ability and the national
importance of his scientific contributions. 
While I am aware of Dr. Nikitin's contributions in several subfields of computer
security and data privacy, I believe that his most outstanding achievements are
in developing techniques for protection of metadata. 
Metadata come in many forms. What resources users access, who they communicate
with, and how they do it constitute sensitive information that is often as
important as the content of the communication itself. 
\textbf{Dr. Nikitin's research focuses on protecting side information exposed
during data encryption and protecting user access patterns—areas that are both
technically challenging and vital to national security and individual privacy. 
As I testified to \ldots, all data are personally identifiable information
because even innocuous-looking data about an individual can be correlated with
her identity.
In an era where cyber threats and mass surveillance pose increasing risks, Dr.
Nikitin's innovations contribute directly to the protection of U.S. 
infrastructure, businesses, and citizens from data exploitation.}}

\bbb, YY at \reduni, highlights the national
importance of \drs research work (see \citewb{letter-bbb}):

\qu{Dr. Nikitin's expertise in data protection and digital privacy is of
national significance to the United States.
In recent years, the U.S. government has increasingly recognized the urgent need
for advancements in privacy-preserving technologies, particularly in response to
escalating cybersecurity threats. 
This has led to a rise in federally funded grant programs dedicated to this
critical area.
\textbf{Dr. Nikitin contributed to a project funded
by the Defense Advanced Research Projects Agency (DARPA), a government agency
focused on developing cutting-edge technologies for national defense.}
As part of this project, he devised techniques for metadata-private
communication that make an individual user's network activity appear
indistinguishable to hostile network observers and render it resistant to
traffic analysis.
\textbf{By continuing his research in the United States, Dr. Nikitin will be
well-positioned to further these vital efforts, advancing technologies that not
only safeguard individual privacy but also strengthen national security and
reinforce our country's leadership in technological innovation.}}

\drs unique background and accomplishments further underscore the substantial
merit and national importance of his work.
With over 10 years of research experience, a Ph.D. from \epfl (ranked as
the 10\textsuperscript{th} best university in the world in Engineering \&
Technology), a M.Sc. from \kth (the 37\textsuperscript{th} best)---globally
top-ranked institutions in computer science---and postdoctoral training at
Cornell University and Columbia University, he brings exceptional expertise to
the field (see \citewb{degrees} for proof of \drs degrees and
\citewb{universities} for the QS World University Rankings).

\aaa, XX at Black University comments on the potential and future job prospects
of \dr (see \citewb{letter-aaa}):

\qu{\ldots}

In summary, \drs contributions are not only timely but essential.
His proposed employment in the United States will drive innovation in fields of
national importance, strengthen the country's leadership in privacy and security
technologies, and advance its strategic objectives in safeguarding digital
infrastructure and promoting economic prosperity.