\renewcommand\refname{List of Exhibits}

\begin{thebibliography}{25}
\label{list-exhibits}

\subsection*{Academic and professional background}
\bibitem{cv} 
Curriculum Vitae of \drfull.

\bibitem{gscholar}
Google Scholar Profile of \drfull.

\subsection*{Letters of support}

\bibitem{letter-aaa}
Letter of support from \aaa (Black University), followed by his CV.

\bibitem{letter-bbb}
Letter of support from \bbb (\reduni), followed by his CV.

\bibitem{letter-ccc}
\emph{Independent} letter of support from \ccc (\blueuni), followed by his CV.

\bibitem{letter-ddd}
\emph{Independent} letter of support from \ddd(\yellowuni), followed by his CV.

\bibitem{letter-eee}
\emph{Independent} letter of support from \eee (\whiteuni), followed by
his CV.

\bibitem{letter-fff}
\emph{Independent} letter of support from \fff (\purpleinc and \cyanuni),
followed by his CV. 

\bibitem{letter-ggg}
\emph{Independent} letter of support from \ggg (\violetinc), followed by his CV.

\bibitem{letter-jjj}
\emph{Independent} letter of support from \jjj (\violetinc), followed by his CV.



\subsection*{Key scientific contributions by \drfull}

\bibitem{thesis}
The title page and abstract of \drs Ph.D. thesis on the protection of metadata
and data integrity.

\bibitem{purbs}
The first pages of the publication by \dr on protecting metadata in encrypted
data and communication, \textbf{alongside the evidence of \drs inventions
being used in Apple's iMessage and in Facebook Messenger}:
\begin{itemize}
	\item \textit{\underline{Nikitin K.}, Barman L., Lueks W., Underwood M., Hubaux J. P., and Ford B. Reducing Metadata Leakage from Encrypted Files and Communication with {PURBs}. Proceedings on Privacy Enhancing Technologies, 2019(4).}
	\item The announcement by Apple Security Engineering and Architecture about
	the changes in iMessage which describes the use of \drs inventions in the
	``Padding and Encryption'' section.
	\item The announcement by Facebook Engineering about upgrading Messenger's
	security which presents the Labyrinth encrypted storage protocol.
	The Labyrinth protocol uses \drs inventions.
	\item Extracts from Labyrinth's documentation that describe the protocol's
	design goals and the use of \drs inventions in the ``2.\,Padding'' section.
	\item Statistics on the number of active users of iMessage and Facebook
	Messenger.
\end{itemize}

\bibitem{apir}
The first pages of the publication by \dr on ensuring data integrity in private
information retrieval:
\begin{itemize}
	\item \textit{Colombo S., \underline{Nikitin K.}, Corrigan-Gibbs H., Wu
	D. J., and Ford B. Authenticated Private Information Retrieval. In USENIX
	Security Symposium 2023.}
\end{itemize}

\bibitem{chainiac}
The first pages of the publication by \dr on securing the software supply chain,
\textbf{alongside the evidence that this work has been included in the
graduate-level curriculum at multiple US and international universities}:
\begin{itemize}
	\item \textit{\underline{Nikitin K.}, Kokoris-Kogias E., Jovanovic P.,
	Gailly N., Gasser L., Khoffi I., Cappos J., Ford B. {CHAINIAC}: Proactive
	{Software-Update} transparency via collectively signed skipchains and
	verified builds. In USENIX Security Symposium 2017.}
	\item A course syllabus from the University of Chicago.
	\item A course syllabus from the University of California, San Diego.
	\item A course syllabus from the University of Illinois at Urbana-Champaign.
	\item A course syllabus from the Technical University of Munich, Germany.
\end{itemize}

\bibitem{blockchain}
The first page of the publication authored by \dr on improving the efficiency of
blockchain networks:
\begin{itemize}
	\item \textit{Lee J., \underline{Nikitin K.}, Setty S. Replicated state
	machines without replicated execution. In {IEEE} Symposium on Security and
	Privacy 2020.}
\end{itemize}

\bibitem{other_papers}
The first page of an additional publication authored by \dr on securing group
communication in the Internet of Things: 
\begin{itemize}
	\item \textit{Tiloca M., \underline{Nikitin K.}, Raza S. Axiom: {DTLS}-based
	secure {IoT} group communication. {ACM} Transactions on Embedded Computing
	Systems ({TECS}), 2017.}
\end{itemize}

\subsection*{Other}

\bibitem{degrees}
Proof of \drfulls advanced degrees (Ph.D., M.Sc., and M.Sc.) in Computer
and Communication Sciences, Information and Communication Technology, and
Information Security, respectively.

\bibitem{venues}
Conference and journal rankings by category.

\bibitem{reviews}
Proof of \numreviews scientific reviews undertaken by \dr in conferences and
journals on data privacy, computer security, and blockchain.

\bibitem{acm_membership}
Proof of \drs membership in the Association for Computing Machinery (ACM) and
in the Institute of Electrical and Electronics Engineers (IEEE).

\bibitem{recomb-prieq}
Evidence that \dr co-organized The Satellite Conference on Biomedical Data
Privacy and Equity (RECOMB-PRIEQ 2024).

\bibitem{media}
Evidence of published material about \drs work in professional and major trade
publications.

\bibitem{universities}
QS World University Rankings.

\bibitem{offers}
The current employment letter and the offer letters that \dr received for postdoctoral researcher positions:
\begin{itemize}
	\item The latest employment extension letter from XX (current).
	\item The offer letters from XX and YY (accepted, currently employed).
	\item The offer letter from ZZ (accepted).
	\item The offer letter from WW (declined).
\end{itemize}

\bibitem{government}
Executive orders, a national strategy report, and an action plan by the federal
government which highlight the national importance of \drs area of research
and proposed employment.
\begin{itemize}
	\item Executive Order on the Safe, Secure, and Trustworthy Development
	and Use of Artificial Intelligence (2023).
	\item National Strategy to Advance Privacy-Preserving Data Sharing
	and Analytics (2023).
	\item National Privacy Research Strategy (2025).
	\item Executive Order on America's Supply Chains (2024).
	\item Executive Order on Improving the Nation's Cybersecurity (2021).
	\item An Action Plan on Securing Defense-Critical Supply Chains (2022).
	\item Executive Order on Strengthening American Leadership in Digital
	Financial Technology (2025).
\end{itemize}

\end{thebibliography}
\pagebreak

\label{exhibits}
\newcommand{\ex}[2]{
	\title{\textbf{\huge{Exhibit #1}}\\
		\vspace{3em}
		\Large{#2}
	}
	\author{}
	\date{}
	\maketitle
	\thispagestyle{fancy} % Use fancy page style
	\fancyhf{} % Clear all header and footer fields
	\fancyhfoffset[L]{1cm} % left extra length
	\fancyhfoffset[R]{1cm} % right extra length
	\renewcommand{\headrulewidth}{1pt}
	\lhead{EB-1A Permanent Residence Petition for \drfull}
	\rfoot{Page \thepage~of \pageref*{LastPage}} % Define right footer
}

\ex{1}{Curriculum Vitae of \drfull}
\newpage

\ex{2}{Google Scholar Profile of \drfull}
\ip{../supporting/pubs/gscholar.pdf}

\ex{3}{Letter of support from \aaa (Black University), followed by his CV}
\newpage

\ex{4}{Letter of support from \bbb (\reduni), followed by his CV}
\ip{../letters/letter-bbb.pdf}

\ex{5}{\emph{Independent} letter of support from \ccc (\blueuni), followed by
his CV}
\ip{../letters/letter-ccc.pdf}

\ex{6}{\emph{Independent} letter of support from \ddd(\yellowuni), followed by
his CV}
\ip{../letters/letter-ddd.pdf}

\ex{7}{\emph{Independent} letter of support from \eee (\whiteuni), followed by
his CV}
\ip{../letters/letter-eee.pdf}

\ex{8}{\emph{Independent} letter of support from \fff
(\purpleinc and \cyanuni), followed by his CV}
\ip{../letters/letter-fff.pdf}

\ex{9}{\emph{Independent} letter of support from \ggg
(\violetinc), followed by his CV}
\newpage

\ex{10}{\emph{Independent} letter of support from \jjj (\violetinc), followed by his CV}
\newpage


\ex{11}{The title page and abstract of \drs Ph.D. thesis on protection of metadata and data integrity}
\ip{../supporting/pubs/thesis.pdf}

\ex{12}{The first pages of the peer-reviewed publication authored by \dr on protecting metadata in encrypted data and communication, alongside evidence of the \drs inventions being used in Apple's iMessage and in Facebook Messenger:}
\vspace{-7em}
\begin{enumerate}
	\item \textit{\underline{Nikitin K.}, Barman L., Lueks W., Underwood M., Hubaux J. P., and Ford B. Reducing Metadata Leakage from Encrypted Files and Communication with {PURBs}. Proceedings on Privacy Enhancing Technologies, 2019(4).}
	\item The announcement by the Apple Security Engineering and Architecture
	team about the changes in iMessage which describes the use of \drs
	inventions in the ``Padding and Encryption'' section.
	\item The announcement by Facebook Engineering about upgrading Messenger's
	security which presents the Labyrinth encrypted storage protocol.
	The Labyrinth protocol uses \drs inventions.
	\item Extracts from Labyrinth's documentation that describe the protocol's
	design goals and the use of \drs inventions in the ``2.\,Padding'' section.
	\item Statistics on the number of active users of iMessage and Facebook
	Messenger.
\end{enumerate}
\ip{../supporting/pubs/purbs.pdf}
\ip{../supporting/pubs/imessage.pdf}
\ip{../supporting/pubs/fb_announcement.pdf}
\ip{../supporting/pubs/fb_labyrinth.pdf}
\ip{../supporting/pubs/imessage_fb_usage.pdf}

\ex{13}{The first pages of the peer-reviewed publication authored by \dr on ensuring data integrity in private information retrieval:}
\vspace{-7em}
\begin{itemize}
	\item \textit{Colombo S., \underline{Nikitin K.}, Corrigan-Gibbs H., Wu
	D. J., and Ford B. Authenticated Private Information Retrieval. In USENIX
	Security Symposium 2023.}
\end{itemize}
\ip{../supporting/pubs/apir.pdf}

\ex{14}{The first pages of the peer-reviewed publication authored by \dr on
securing the software supply chain, alongside the evidence that this work has
been included in the graduate-level curriculum at multiple US and international
universities:}
\begin{itemize}
	\item \textit{\underline{Nikitin K.}, Kokoris-Kogias E., Jovanovic P.,
	Gailly N., Gasser L., Khoffi I., Cappos J., Ford B. {CHAINIAC}: Proactive
	{Software-Update} transparency via collectively signed skipchains and
	verified builds. In USENIX Security Symposium 2017.}
	\item Course syllabi from the following universities (the entires about \drs work are
	highlighted):
	\begin{itemize}
		\item The University of Chicago
		\item The University of California, San Diego
		\item The University of Illinois at Urbana-Champaign
		\item The Technical University of Munich, Germany
	\end{itemize}
\end{itemize}
\ip{../supporting/pubs/chainiac.pdf}
\ip{../supporting/chainiac/uchicago.pdf}
\ip{../supporting/chainiac/ucsd.pdf}
\ip{../supporting/chainiac/uiuc.pdf}
\ip{../supporting/chainiac/tum.pdf}

\ex{15}{The first page of the peer-reviewed publication authored by \dr on improving the efficiency of blockchain networks}
\vspace{-7em}
\begin{itemize}
	\item \textit{Lee J., \underline{Nikitin K.}, Setty S. Replicated state
	machines without replicated execution. In {IEEE} Symposium on Security and
	Privacy 2020.}
\end{itemize}
\ip{../supporting/pubs/piperine.pdf}

\ex{16}{The first page of an additional peer-reviewed publication authored by
\dr on securing group communication in the Internet of Things}
\vspace{-7em}
\begin{itemize}
	\item \textit{Tiloca M., \underline{Nikitin K.}, Raza S. Axiom: {DTLS}-based
	secure {IoT} group communication. {ACM} Transactions on Embedded Computing
	Systems ({TECS}), 2017.}
\end{itemize}
\ip{../supporting/pubs/axiom.pdf}

\ex{17}{Proof of \drfulls advanced degrees (Ph.D., M.Sc., and M.Sc.) in Computer
and Communication Sciences, Information and Communication Technology, and
Information Security}
\vspace{-7em}
\begin{itemize}
	\item An academic credentials report by Foreign Credentials Service of
	America, a member of National Association of Credential Evaluation Services  (NACES), certifying the U.S. equivalency of \drs degrees
	\item The Doctor of Science (Ph.D.) degree in Computer and Communication Sciences from \epfl
	\begin{itemize}
		\item The Ph.D. diploma, alongside its official translation to English
		by the university, and the transcript
	\end{itemize}
	\item The Master of Science (M.Sc.) degree in Information and Communication Technology from \kth
	\begin{itemize}
		\item The degree certificate and the transcript, in both Swedish and English
	\end{itemize}
	\item The Specialist (M.Sc.) degree in Information Security from Kazan Federal University, Russia
	\begin{itemize}
		\item The degree certificate and the transcript, alongside their
		official translation to English by the university
	\end{itemize}
\end{itemize}
\newpage

\ex{18}{Conference and journal rankings by category:}
\vspace{-7em}
\begin{enumerate}
	\item Top Conferences for Computer Security and Cryptography
	\item Top Journals for Computer Security and Cryptography
	\item Top Journals for Databases and Information Systems
	\item h5-index of Top conferences and journals for Computer Security and Cryptography
	\item h5-index of top conferences and journals for Computing systems
	\item h5-index of top conferences and journals for general Engineering and Computer Science
	\item The ranking of the ACM Conference on Computer and Communications Security (CCS)
	\item The ranking of the USENIX Security Symposium
	\item The ranking of the IEEE Symposium on Security and Privacy (S\&P)
	\item The ranking of the Privacy Enhancing Technologies Symposium (PETS)
	\item The ranking of the ACM Transactions on Embedded Computing Systems (TECS)
	\item The ranking of the IEEE International Conference on Blockchain and Cryptocurrency (ICBC)
   \end{enumerate}
\ip{../supporting/venues/research.com_conferences_sec.pdf}
\ip{../supporting/venues/research.com_journals_sec.pdf}
\ip{../supporting/venues/research.com_journals_db.pdf}
\ip{../supporting/venues/gscholar_sec.pdf}
\ip{../supporting/venues/gscholar_compute.pdf}
\ip{../supporting/venues/gscholar_general.pdf}
\ip{../supporting/venues/ccs.pdf}
\ip{../supporting/venues/usesec.pdf}
\ip{../supporting/venues/sp.pdf}
\ip{../supporting/venues/pets.pdf}
\ip{../supporting/venues/tecs.pdf}
\ip{../supporting/venues/icbc.pdf}

\ex{19}{Proof of \numreviews scientific reviews undertaken by \dr in conferences
and journals on data privacy, computer security, and blockchain}
\vspace{-7em}
\begin{itemize}
	\item (32 reviews) The ACM Conference on Computer and Communications Security (CCS)
	\begin{itemize}
		\item The invitation to join the Program Committee of the
		conference in year 2024, a submission page that lists 8 reviews by \dr
		in Cycles A and B of the conference, and copies of the submitted
		reviews.
		\item The invitation to join the Program Committee of the
		conference in year 2023, a submission page that lists 6 reviews by \dr,
		and copies of the submitted reviews.
		\item The invitation to join the Program Committee of the
		conference in year 2021, a submission page that lists 17 reviews by \dr,
		and copies of the submitted reviews.
		\item The invitation to provide an expert review for an additional
		submission to ACM CSS 2021, and a copy of the review submitted by \dr.
	\end{itemize}
	\item (16 reviews) The invitation to join the Program Committee of the
	USENIX Security Symposium in year 2025, a submission page that lists 8
	reviews in Cycle 1 and 4 reviews in Cycle 2 by \dr, and copies of the submitted reviews.
	\item (1 review) The invitation to provide an expert review for
	Eurocrypt 2022, and a copy of the review submitted by \dr.
	\item (6 reviews) The invitation to join the Program Committee of the
	IEEE International Conference on Blockchain and Cryptocurrency (ICBC) in
	year 2019, a submission page that lists 6 reviews by \dr, and copies of
	the submitted reviews.
	\item (1 review) The invitation to provide an expert review for a
	submission to the IEEE Transactions on Industrial Informatics (TII), and a
	confirmation of the review submitted by \dr.
	\item (2 reviews) Two invitations to provide an expert review for
	submissions to the IEEE Transactions on Parallel and Distributed Systems (TPDS)
	and copies of the reviews submitted by \dr.
	\item (2 reviews) The invitations to provide an expert review for a submission to the International Conference on Research in Computational Molecular Biology (RECOMB), and copies of the reviews submitted by \dr.
	\item (1 review) The invitation to provide an expert review for a
	submission to the Annual International Conference on Intelligent Systems for
	Molecular Biology (ISMB), and a copy of the review submitted by \dr.
	\item (5 reviews) The invitations to join the Program Committee of the
	Workshop on Cryptocurrencies and Blockchains for Distributed Systems
	(CryBlock) in the years 2019 and 2020, the submission pages that list the
	reviews by \dr and copies of the reviews.
	\item (2 reviews) The invitation to join the Program Committee of the
	International Conference on Blockchain and Trustworthy Systems (BlockSys) in
	the year 2019, a submission page that lists 2 reviews by \dr, and copies of
	the submitted reviews.
\end{itemize}


\ex{20}{Proof of \drs membership in the Association for Computing Machinery (ACM) and in the Institute of Electrical and Electronics Engineers (IEEE)}

\ex{21}{Evidence that \dr co-organized The Satellite Conference on Biomedical Data Privacy and Equity (RECOMB-PRIEQ 2024). \drs name appears at the top of the Program Committee list with the track chair role.}

\ex{22}{Evidence of published material about \drs work in professional and major trade publications:}
\vspace{-7em}
\begin{itemize}
	\item An article published by ZDNET on Padded Uniform Random Blobs, \drs
	inventions for protection of encryption metadata.
	\item Statistics by semrush.com on the readership of ZDNET.
	\item A Wikipedia article about the same invention, which provides more
	in-depth overview of techniques and their applications.
	\item An article published by CyberScoop on \drs work on security of
	software-update systems.
	\item An article published by The 311 Institute on \drs work on security of
	software-update systems.
	\item An excerpt from Google Scholar listing the prominent scientific
	surveys that review \drs work on securing IoT group communication.
	\item A post in the popular computer science blog ``The Morning Paper'' that covers \drs work on securing software-update systems.
\end{itemize}
\ip{../supporting/media/purbs_zdnet.pdf}
\ip{../supporting/media/zdnet_traffic.pdf}
\ip{../supporting/media/purbs_wikipedia.pdf}
\ip{../supporting/media/chainiac_cyberscoop.pdf}
\ip{../supporting/media/chainiac_311institute.pdf}
\ip{../supporting/media/axiom_citations.pdf}
\ip{../supporting/media/chainiac_morning_paper.pdf}

\ex{23}{QS World University Rankings}
\vspace{-7em}
The universities and their respective world rankings where \drfull obtained his
advanced degrees and conducted research activity as a postdoctoral scientist:
\begin{itemize}
	\item The QS World University Rankings 2025: Top global universities.
	\begin{itemize}
		\item Cornell University is ranked 16th (the university of \drs first
		postdoctoral employment).
		\item \'Ecole polytechnique f\'ed\'erale de Lausanne is ranked 26th (the
		university from which \dr obtained his Ph.D. degree).
		\item Columbia University is ranked 34th (the university of \drs current
		postdoctoral employment).
	\end{itemize}
	\item The QS World University Rankings by Subject 2024: Engineering \&
	Technology.
	\begin{itemize}
		\item \'Ecole polytechnique f\'ed\'erale de Lausanne is ranked 10th (the
		university from which \dr obtained his Ph.D. degree).
		\item Cornell University is ranked 30th (the university of \drs first
		postdoctoral employment).
		\item KTH Royal Institute of Technology is ranked 37th (the university
		from which \dr obtained his MS degree).
		\item Columbia University is ranked 44th (the university of \drs current
		postdoctoral employment).
	\end{itemize}
\end{itemize}
\ip{../supporting/rankings/global.pdf}
\ip{../supporting/rankings/subject.pdf}

\ex{24}{The current employment letter and the offer letters that \dr received for postdoctoral researcher positions:}
\vspace{-7em}
\begin{enumerate}
	\item The latest employment extension letter from XX (current).
	\item The offer letters from XX and YY (accepted, currently employed).
	\item The offer letter from ZZ (accepted).
	\item The offer letter from WW (declined).
\end{enumerate}

\ex{25}{Executive orders, a national strategy report, and an action plan by the
federal government which highlight the national importance of \drs area of
research and proposed employment:}
\vspace{-7em}
\begin{itemize}
	\item Executive Order on the Safe, Secure, and Trustworthy Development
	and Use of Artificial Intelligence, 2023 (the opening page).
	\item National Strategy to Advance Privacy-Preserving Data Sharing
	and Analytics, 2023 (the title page, the table of contents, the executive
	summary, and page 18).
	\item National Privacy Research Strategy, 2025 (the title page, the table of
	contents, and the executive summary).
	\item Executive Order on America's Supply Chains, 2024 (the opening page).
	\item Executive Order on Improving the Nation's Cybersecurity, 2021 (the
	opening page).
	\item An Action Plan on Securing Defense-Critical Supply Chains, 2022 (the title page, the table of contents, and the executive summary).
	\item Executive Order on Strengthening American Leadership in Digital
	Financial Technology, 2025 (the opening page).
\end{itemize}
\ip{../supporting/government/order-secure-ai.pdf}
\ip{../supporting/government/national-privacy-strategy.pdf}
\ip{../supporting/government/order-supply-chains.pdf}
\ip{../supporting/government/order-cybersecurity.pdf}
\ip{../supporting/government/action-plan-supply-chains.pdf}
\ip{../supporting/government/order-digital-finance.pdf}