%!TEX root = ./main.tex
\subsection{Evidence of the published material in professional or major 
	trade publications or other major media about \drs work in the field}
\label{sec:media}

One of the key indicators of extraordinary ability is the publication of
material about the individual's work in professional, major trade
publications, or other major media outlets.
\drs work in \dpcs has garnered substantial recognition in both industry and
media, demonstrating the impact and significance of his contributions.
Below are some examples of such published material:

\begin{itemize}
	\item \textbf{ZDNET:} ZDNET.com, a highly respected global platform for
	technology news and analysis, has published material about \drs
	work on protection of encryption metadata, specifically on Padded
	Uniform Random Blobs (PURBs), the encrypted-data format devised by
	\dr.
	According to semrush.com, ZDNET.com receives over 24 million visits per
	month, with a significant portion of its readership being IT
	professionals, industry leaders, and decision-makers across the globe,
	which ranks it among the top technology news websites in the
	world (see \citewb{media} for ZDNET.com's article about \drs work and the statistics on ZDNET.com's readership).
	The coverage by ZDNET.com highlights the innovative nature of \drs work,
	particularly in Data Privacy, and its potential to impact the broader
	tech landscape.
	\item \textbf{Wikipedia:} A Wikipedia article about Padded
	Uniform Random Blobs (PURBs) has been published, providing an independent
	and widely accessible overview of his work~\cite[A Wikipedia
	article]{media}.
	Wikipedia is a globally recognized source of information, and the
	existence of a dedicated article signifies the public interest and the
	relevance of \drs invention, which further demonstrates the broad impact and recognition of his work.
	\item \textbf{CyberScoop:} An article about \drs work on security of
	software-update systems	appeared on CyberScoop.com, a leading media
	outlet that focuses on cybersecurity news and insights with more 6
	million unique monthly engagements~\cite[CyberScoop's article about a
	framework devised by \dr]{media}.
	Their coverage has delved into the technical aspects and implications of
	\drs work, reinforcing his standing as a key innovator in the industry.
	\item \textbf{The 311 Institute:} In addition to ZDNET and CyberScoop, 
	The 311 Institute, a future-focused research and technology platform,
	has also recognized \drs contributions.
	Its article has reviewed \drs work on the security of software-update
	systems, acknowledging its potential to drive significant advancements
	in Computer Security~\cite[The 311 Institute's atricle about a framework
	devised by \dr]{media}.
\end{itemize}

\aaa, XX at Black University
describes the appearances of \drs work in major media outlets in
his letter of support (see \cite{letter-aaa}):

\qu{In addition to the industry adoption, Dr. Nikitin's work has received
significant media attention. 
His work on PURBs, for example, has been featured on ZDNET.com---a large
international online media that covers groundbreaking innovations in technology.
The published article acknowledged that PURBs pointed the way for rearchitecting
encryption suites to dramatically improve security. 
Similarly, the work on CHAINIAC has been featured in CyberScoop---another
leading public-sector media that reports on news and events impacting technology
and security.
\textbf{This level of media coverage demonstrates that Dr. Nikitin's work
resonates far beyond the confines of the academic community. 
His contributions are shown to address issues of critical relevance to both
industry professionals and the general public.}}

\paragraph{Reviews by other experts and researchers.}
\drs work has also been cited by numerous published scientific articles
within the field of \dpcs~\cite[Google Scholar profile of \dr]{gscholar}.
For instance, \drs work on securing group communication in the Internet Of
Things has been featured in several highly-cited surveys of the field's
challenges and prominent solutions~\cite[Publications that review \drs
work]{media}.
Similarly, \drs work on securing software-update systems has been featured
in The Morning Paper, a popular blog provides short summaries of important, 
influential, topical or otherwise interesting papers in the field of computer 
science~\cite{media}.

\textbf{The recognition of \drs work in these major media outlets, combined 
with the citations by other experts and researchers, highlights \drs 
extraordinary ability and significant role in advancing the field of \dpcs. 
These publications serve as objective evidence of the widespread impact of \drs 
work and its importance to the global community.}