%!TEX root = ./main.tex
\section{Final merits determination}
\label{sec:merits}

In accordance with the Kazarian opinion, the second step of the two-part
approach is a final merits determination that considers all of the evidence in
the context of whether the beneficiary meets the required level of high
achievement and sustained international reputation in the field.
The aggregated evidence establishes that \dr not only meets at least four of the
regulatory criteria, but also that he has been recognized internationally as
outstanding in his field of expertise.

Throughout his professional career, \dr has made numerous critical discoveries
that have advanced the field. These groundbreaking contributions are detailed
above and have been corroborated by internationally recognized experts in the
field (see \citewb{letter-aaa}-\citewb{letter-jjj}).
\textbf{As these experts confirm, \dr has made original contributions with 
wide-reaching practical applications throughout his research career.}
His work on metadata protection has been adopted by iMessage
and Facebook Messenger, real-world systems with over billion
users (\cref{sec:purbs}), 
his work on private information retrieval has addressed a long-lasting security
flaw in the design of existing schemes and has started a new line of research in
the field (\cref{sec:apir}),
his work on the security of software supply-chain has been highly cited by other
researchers and has been used in graduate-level courses at various
universities (\cref{sec:chainiac}),
and, finally, his work on the efficiency of blockchain networks was the first to
demonstrate the practical benefits of verifiable computation
(\cref{sec:blockchain}).

\textbf{\dr is a scientist of extraordinary ability, who is recognized to have risen to the very top of the field of his expertise.}
He has both published his research findings in and judged the work of other
researchers in the most prestigious, top-ranked conference proceedings and
journals.
Concretely, \dr has published in or served on the program committee of
each of the top three venues in \dpcs, according to Research.com and Google
Scholar Metrics (see \citewb{venues} for the rankings).
His work has been cited \numcitations times by other scientists worldwide
(\cref{sec:authorship}) and has been covered by major media outlets
(\cref{sec:media}).
He has completed \numreviews~full-length reviews for
the top conferences and journals in the field (\cref{sec:judging}).

\paragraph{\dr has not only had contributions of international acclaim, but has also sustained them.}
His publications were cited 50+ times in the past year alone, more than in
any year prior.
\dr continues to be invited to participate in the program committees of the
top conferences and receives invitations to review articles from the top
journals in his field.
Just recently, he organized The Satellite Conference on Biomedical
Data Privacy and Equity 2024, a highly specialized conference for scientists
working on the privacy of biomedical data, which confirmed his
standing in the field.

\dr's work has both substantial merit and national importance for the
United States, as his work aligns with national priorities in strengthening the
country's leadership in privacy and security technologies.
The totality of the presented evidence clearly shows that \dr has been
internationally recognized as outstanding in the field.
As such, \dr meets the requirements for the EB-1A classification as a person of
extraordinary ability in sciences.

